---
title: "Assignment 6: Under (blood) pressure"
author: MinJae Jo
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(modelr))
# Load dataset
blood_pressure <- read_rds("blood_pressure.rds")
```

## Exercise 1
```{r, echo=FALSE}
blood_pressure %>%
  pivot_longer(cols = Age:Pulse, names_to = "measurement", values_to = "value") %>%
  ggplot() +
  geom_point(aes(x = value, y = Systol)) +
  geom_smooth(aes(x = value, y = Systol), method = "lm") +
  facet_wrap(~ measurement, scales = "free_x")
```


## Exercise 2

i) Years graph, the blue regression line tilts slightly down. Therefore, there is a weak negative correlation between Years and Systol.

ii) Forearm and Calf also show positive slopes, but Weight is the largest and most pronounced. Therefore, the answer is Weight.

## Exercise 3

```{r}
blood_pressure_updated <- blood_pressure %>%
  mutate(urban_frac_life = Years / Age)
```


## Exercise 4




## Exercise 5




## Exercise 6




## Exercise 7




## Exercise 8




## Exercise 9




## Exercise 10




## Exercise 11




## Exercise 12



## Academic Integrity statement