---
title: "Assignment 3: Volcanic Eruptions"
author: MinJae Jo
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: tibble
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: tibble
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
```

```{r}
eruptions <- read_csv("eruptions_dataset.csv")
```

## Exercise 1
CSV (Comma-Separated Values) is a simple text format that stores data separated by commas. Each row represents one record (observation), and each column represents a variable (attribute). The file size is small and it is easy to read and write in various tools such as Excel, R, and Python, so it is highly compatible. However, if commas are included in the value, attention should be paid to quotation processing, encoding differences, and line modulation problems.


## Exercise 2



## Exercise 3



## Exercise 4



## Exercise 5



## Exercise 6



## Exercise 7



## Exercise 8



## Exercise 9