---
title: "Assignment 1: R Markdown practice"
author: "MinJae Jo"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: true
    smart: true
    dev: svg
urlcolor: blue
---

```{r setup, include=FALSE}
# Get GitHub username
if (.Platform$OS.type == "unix") {
  git_remote <- system('git config --get remote.origin.url', intern = TRUE)
  git_user <- (strsplit(git_remote, "assignment-1-") |> unlist())[2]
} else {
  git_remote <- shell('git config --get remote.origin.url', intern = TRUE)
  git_user <- (strsplit(git_remote, "assignment-1-") |> unlist())[2]
}
```

---
subtitle: "GitHub username: Asher139"
---

# Hello World!
## Hello World!
### Hello World!

*italics* or _italics_  
**bold** or __bold__  
***bold and italicized***

- Bullet point item
- Second item
    - Sub-list indented by 4 spaces
    + Different bullet point symbol
    - Another bullet point symbol
        * Sub-sub-list

1. Numeric list
2. Second item
    i. Roman numeral sub-list
        a. A sub-sub-list

Consecutive  
lines  
become a single paragraph

unless you leave a blank line between them.

[Link](https://www.google.com)

Math equation: $C = 2 \pi r$

Inline code: Two plus two equals `r 2+2`

```{r}
2 + 2
```
