---
title: "Final Project"
author: "MinJae Jo"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(infer))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(broom))
# Load dataset
college <- read_rds("college.rds") %>%
  type_convert(
    na=combine("", "NA", "PrivacySuppressed")
  )
# Set seed
set.seed(98261936)
```

## Introduction
Introduction

For this project, I am looking at the question: “Does the size or competitiveness of a college affect its degree attainment rate?” I chose C150_4 as my response variable because it shows the share of students who finish their degree within 150% of the usual time. It is one of the clearer numbers in the dataset that relates to graduation.

For the explanatory variable, I am using SAT_AVG. The SAT score is not exactly the same as college size, but schools with higher SAT averages usually have more selective admissions and sometimes bigger or more competitive environments. So I thought it could work as a way to compare colleges that are different in scale or difficulty.

Both variables are continuous, so I am planning to use a linear model to see if they move together in some way. I think this topic is interesting. People often talk about whether large schools or hard-to-select schools help students succeed, but it is hard to know without seeing the data in person. I would like to see what the CollegeScorecard dataset actually shows.

## Preprocessing
```{r, echo=FALSE}
college_reduced <- college %>%
  select(C150_4, SAT_AVG)
college_reduced <- college_reduced %>%
  rename(
    grad_rate_150 = C150_4,
    sat_avg = SAT_AVG
  )
summary(college_reduced)
```


## Visualization
Summary statistics for graduation rate (C150_4)
```{r, echo=FALSE, warning=FALSE}
college_reduced %>%
  summarise(
    n_grad = n(),
    mean_grad = mean(grad_rate_150, na.rm = TRUE),
    median_grad = median(grad_rate_150, na.rm = TRUE),
    sd_grad = sd(grad_rate_150, na.rm = TRUE),
    iqr_grad = IQR(grad_rate_150, na.rm = TRUE),
    min_grad = min(grad_rate_150, na.rm = TRUE),
    max_grad = max(grad_rate_150, na.rm = TRUE)
  )
```
-The graduation rate values range from 0 to 1. The median is around 0.49, so about half of the colleges graduate less than half of their students on time. This suggests that many schools are kind of in the middle rather than extremely high or low.


Summary statistics for SAT_AVG
```{r, echo=FALSE, warning=FALSE}
college_reduced %>%
  summarise(
    n_sat = n(),
    mean_sat = mean(sat_avg, na.rm = TRUE),
    median_sat = median(sat_avg, na.rm = TRUE),
    sd_sat = sd(sat_avg, na.rm = TRUE),
    iqr_sat = IQR(sat_avg, na.rm = TRUE),
    min_sat = min(sat_avg, na.rm = TRUE),
    max_sat = max(sat_avg, na.rm = TRUE)
  )

```
-The SAT averages go from the mid-500s to around 1550. The median is about 1116, which means most schools are not super selective, but not weak either. The scores are pretty spread out, so colleges in this dataset vary a lot in competitiveness.

Graduation Rate of Histogram
```{r, echo=FALSE, warning=FALSE}
ggplot(college_reduced, aes(x = grad_rate_150)) +
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black") +
  labs(
    title = "Distribution of Graduation Rate (within 150% time)",
    x = "Graduation Rate (C150_4)",
    y = "Count"
  )
```
SAT Average of Histogram
```{r, echo=FALSE, warning=FALSE}
ggplot(college_reduced, aes(x = sat_avg)) +
  geom_histogram(binwidth = 50, fill = "lightgreen", color = "black") +
  labs(
    title = "Distribution of SAT Average Scores",
    x = "SAT Average",
    y = "Count"
  )
```
Graduation Rate of Boxplot
```{r, echo=FALSE, warning=FALSE}
ggplot(college_reduced, aes(y = grad_rate_150)) +
  geom_boxplot(fill = "orange") +
  labs(
    title = "Boxplot of Graduation Rate",
    y = "Graduation Rate"
  )
```
## Summary Statistics




## Data Analysis




## Conclusion