---
title: "Final Project"
author: "MinJae Jo"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(infer))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(broom))
# Load dataset
college <- read_rds("college.rds") %>%
  type_convert(
    na=combine("", "NA", "PrivacySuppressed")
  )
# Set seed
set.seed(98261936)
```

## Introduction
Introduction

For this project, I am looking at the question: “Does the size or competitiveness of a college affect its degree attainment rate?” I chose C150_4 as my response variable because it shows the share of students who finish their degree within 150% of the usual time. It is one of the clearer numbers in the dataset that relates to graduation.

For the explanatory variable, I am using SAT_AVG. The SAT score is not exactly the same as college size, but schools with higher SAT averages usually have more selective admissions and sometimes bigger or more competitive environments. So I thought it could work as a way to compare colleges that are different in scale or difficulty.

Both variables are continuous, so I am planning to use a linear model to see if they move together in some way. I think this topic is interesting. People often talk about whether large schools or hard-to-select schools help students succeed, but it is hard to know without seeing the data in person. I would like to see what the CollegeScorecard dataset actually shows.

## Preprocessing
```{r, echo=FALSE}
college_reduced <- college %>%
  select(C150_4, SAT_AVG)
college_reduced <- college_reduced %>%
  rename(
    grad_rate_150 = C150_4,
    sat_avg = SAT_AVG
  )
summary(college_reduced)
```


## Visualization




## Summary Statistics




## Data Analysis




## Conclusion